---
title: "Networks - FAPERJ Data"
output: html_notebook
---

```{r}
library(tidyverse)
library(metricshelpr)
library(tools)
library(cowplot)
library(scales)
library(readxl)

EXTRACTED_DATA_PATH = "../../data/extracted-author-data/extracted_author_data-faperj 02-04-2021.RData"

if (file_ext(EXTRACTED_DATA_PATH) == "csv") {
  AUTHOR_DATA = read.table(EXTRACTED_DATA_PATH, header = T, sep = ";", dec = ",")
} else if (file_ext(EXTRACTED_DATA_PATH) %in% c("RData", "Rdata")) {
  load(EXTRACTED_DATA_PATH)
}

AUTHOR_DATA = AUTHOR_DATA %>% mutate(
  ShortName = ShortName %>%
           str_replace("& Preg", "&\nPreg") %>%
           str_replace("& Surv", "&\nSurv") %>%
           str_replace("& Diag", "&\nDiag")
)

AUTHOR_DATA_PATH = "../../data/authors-faperj-call"

GEO_DATA = read_excel("../../data/institutions/Institutions and States - manual curation.xlsx", sheet = 3)
states_list = GEO_DATA %>% pull(State)
regions_list = GEO_DATA %>% pull(Region) %>% unique()
rm(GEO_DATA)

# ggplot theme
ggtheme = theme_cowplot()
theme_set(ggtheme)

source("plot-functions.R")
source("net-functions.R")
```

Load bibliometric data for each author, add columns for target author, affiliation, state and region and if papers were before or after 2016.
```{r}
filenames = paste0(AUTHOR_DATA_PATH, "/", list.files(AUTHOR_DATA_PATH, "txt$"))
# i = which(filenames == paste0(AUTHOR_DATA_PATH, "/Carlos Roberto Prudencio.txt"))
# AUTHOR_NET_DATA = map_dfr(filenames[i:length(filenames)], load_biblio_geo)
AUTHOR_NET_DATA = map_dfr(filenames, load_biblio_geo)
```

Add columns to indicate the Rede FAPERJ for each author.
```{r}
authors_redes_FAPERJ = tibble(
  TargetAuthor = c("Mário Alberto Cardoso da Silva Neto", "Richard Ian Samuels", "Ricardo Lourenço de Oliveira", "Izabel Christina Nunes de Palmer Paixão", "Andrea Thompson da Poian", "Stevens Kastrup Rehen", "Wilson Savino", "Jose Garcia Ribeiro Abreu Junior", "Amilcar Tanuri", "José Mauro Peralta", "Cristina Barroso Hofer", "Marzia Puccioni Sohler"),
  FAPERJ_Network = rep(c(1,2,3,4,5,6), each = 2),
  FAPERJ_NetworkSize = rep(c(31,53,51,111,53,26), each = 2)
)

AUTHOR_NET_DATA = merge(AUTHOR_NET_DATA, authors_redes_FAPERJ, by = "TargetAuthor")
```

When a paper appears more than once, it is a collaboration - merge the states, regions and affiliations. Consider only the five-year period before 2016, to be comparable to the period since the outbreak.
```{r}
AUTHOR_NET_DATA_NC = AUTHOR_NET_DATA
nets = build_period_nets(AUTHOR_NET_DATA_NC)
```

Network metrics.
```{r}
metrics = rbind(
  nets$pre$metrics %>% mutate(Class = "Pre-Outbreak"),
  nets$post$metrics %>% mutate(Class = "Post-Outbreak")
)
metrics
```

Plot the geographical networks.

#### Researchers

```{r}
plot_collab_matrix(nets$pre$edgelist, "Researcher", include_loops = T)
plot_collab_matrix(nets$post$edgelist, "Researcher", include_loops = T)

plot_collab_matrix(nets$pre$edgelist, "FAPERJ_Network", include_loops = T, flevels = as.character(1:6))
plot_collab_matrix(nets$post$edgelist, "FAPERJ_Network", include_loops = T, flevels = as.character(1:6))
```


