---
title: "Analysis and Plots - CNPq data"
output: html_notebook
---

```{r}
library(tidyverse)
library(metricshelpr)
library(tools)
library(cowplot)
library(scales)

EXTRACTED_DATA_PATH = "../../data/extracted-authors-general/extracted_author_data-cnpq 10-03-2021.RData"

# Load data
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

if (file_ext(EXTRACTED_DATA_PATH) == "csv") {
  AUTHOR_DATA = read.table(EXTRACTED_DATA_PATH, header = T, sep = ";", dec = ",")
} else if (file_ext(EXTRACTED_DATA_PATH) %in% c("RData", "Rdata")) {
  load(EXTRACTED_DATA_PATH)
}

AUTHOR_DATA = AUTHOR_DATA %>% mutate(
  ShortName = ShortName %>%
           str_replace("& Preg", "&\nPreg") %>%
           str_replace("& Surv", "&\nSurv") %>%
           str_replace("& Diag", "&\nDiag")
)

# ggplot theme
ggtheme = theme_cowplot()
theme_set(ggtheme)

source("plot_functions.R")
```

## Characterization of the authors who published in Zika

### Description of Most Common Journal Area before Epidemics
```{r}
plot_most_common_areas_before(AUTHOR_DATA, period = "Pre-Outbreak")
```


### Academic Age - Years Since the First Paper Record
```{r}
plot_academic_age_hist(AUTHOR_DATA, period = "Pre-Outbreak")
```

### Total Citations, before Epidemics
```{r}
plot_total_citations(AUTHOR_DATA, period = "Pre-Outbreak", logscale = F)
plot_total_citations(AUTHOR_DATA, period = "Pre-Outbreak", logscale = T)
```

## Changes in publication patterns after the outbreak

```{r}
# Make list of authors with at least 3 papers in each period, so that the estimates have a minimal sample size, to remove a bit of noise
selected_authors = AUTHOR_DATA %>%
  filter(ShortName == "Papers", Class %in% c("Pre-Outbreak", "Zika")) %>%
  mutate(Value = as.numeric(Value)) %>%
  pivot_wider(id_cols = Author, values_from = Value, names_from = Class) %>%
  filter(`Pre-Outbreak` > 3, Zika > 3) %>% pull(Author)
```


### Citations per Paper, before and Zika papers
```{r}
plot_compare_citations_per_paper(AUTHOR_DATA %>% filter(Author %in% selected_authors))
```

### Number of Authors per Paper, before and Zika papers
```{r}
plot_compare_authors_per_paper(AUTHOR_DATA %>% filter(Author %in% selected_authors))
```


### Percentage of Papers with International Affiliations, before and Zika papers
```{r}
plot_compare_intl_papers(AUTHOR_DATA %>% filter(Author %in% selected_authors))
```

### Percentage of Zika-related papers post 2016
```{r}
plot_perc_zika_papers(AUTHOR_DATA)
```

## Characterization of Zika-related publications

### Frequency of MeSH Categories

```{r}
plot_pubs_by_mesh_cat(AUTHOR_DATA, title = "All Fields")
```
### Citations by MeSH category

```{r}
plot_cites_by_mesh_cat(AUTHOR_DATA)
```

### Citations per paper, by MeSH category

```{r}
plot_cite_rate_by_mesh_cat(AUTHOR_DATA)
```

### Which authors published in which categories?

```{r}
plot_pubs_by_mesh_cat_by_field(AUTHOR_DATA)
```

