---
title: "Networks - CNPq Data"
output: html_notebook
---

```{r}
library(tidyverse)
library(metricshelpr)
library(tools)
library(cowplot)
library(scales)
library(readxl)

EXTRACTED_DATA_PATH = "../../data/extracted-author-data/extracted_author_data-cnpq 18-03-2021.RData"

if (file_ext(EXTRACTED_DATA_PATH) == "csv") {
  AUTHOR_DATA = read.table(EXTRACTED_DATA_PATH, header = T, sep = ";", dec = ",")
} else if (file_ext(EXTRACTED_DATA_PATH) %in% c("RData", "Rdata")) {
  load(EXTRACTED_DATA_PATH)
}

AUTHOR_DATA = AUTHOR_DATA %>% mutate(
  ShortName = ShortName %>%
           str_replace("& Preg", "&\nPreg") %>%
           str_replace("& Surv", "&\nSurv") %>%
           str_replace("& Diag", "&\nDiag")
)

AUTHOR_DATA_PATH = "../../data/authors-cnpq-call"

GEO_DATA = read_excel("../../data/institutions/Institutions and States - manual curation.xlsx", sheet = 3)
states_list = GEO_DATA %>% pull(State)
regions_list = GEO_DATA %>% pull(Region) %>% unique()
rm(GEO_DATA)

# ggplot theme
ggtheme = theme_cowplot()
theme_set(ggtheme)

source("plot-functions.R")
source("net-functions.R")
```

Load bibliometric data for each author, add columns for target author, affiliation, state and region and if papers were before or after 2016.
```{r}
filenames = paste0(AUTHOR_DATA_PATH, "/", list.files(AUTHOR_DATA_PATH, "txt$"))
# i = which(filenames == paste0(AUTHOR_DATA_PATH, "/Carlos Roberto Prudencio.txt"))
# AUTHOR_NET_DATA = map_dfr(filenames[i:length(filenames)], load_biblio_geo)
AUTHOR_NET_DATA = map_dfr(filenames, load_biblio_geo)
```

When a paper appears more than once, it is a collaboration - merge the states, regions and affiliations. Consider only the five-year period before 2016, to be comparable to the period since the outbreak.
```{r}
AUTHOR_NET_DATA_NC = AUTHOR_NET_DATA
AUTHOR_NET_DATA = consolidate_biblio_rows(AUTHOR_NET_DATA)
```
Build the networks.
```{r}
nets = build_period_nets(AUTHOR_NET_DATA_NC)
```

Network metrics.
```{r}
metrics = rbind(
  nets$pre$metrics %>% mutate(Class = "Pre-Outbreak"),
  nets$post$metrics %>% mutate(Class = "Post-Outbreak")
)
metrics
```

Plot the geographical networks.

#### States

```{r}
plot_collab_matrix(nets$pre$edgelist, "State", include_loops = T, flevels = states_list)
plot_collab_matrix(nets$post$edgelist, "State", include_loops = T, flevels = states_list)
```

#### Regions

```{r}
plot_collab_matrix(nets$pre$edgelist, "Region", include_loops = T, flevels = regions_list)
plot_collab_matrix(nets$post$edgelist, "Region", include_loops = T, flevels = regions_list)
```
