---
title: "Analysis and Plots - FAPERJ Data"
output: html_notebook
---

```{r}
library(tidyverse)
library(metricshelpr)
library(tools)
library(cowplot)
library(scales)
library(readxl)

EXTRACTED_DATA_PATH = "../../data/extracted-author-data/extracted_author_data-faperj 02-04-2021.RData"

if (file_ext(EXTRACTED_DATA_PATH) == "csv") {
  AUTHOR_DATA = read.table(EXTRACTED_DATA_PATH, header = T, sep = ";", dec = ",")
} else if (file_ext(EXTRACTED_DATA_PATH) %in% c("RData", "Rdata")) {
  load(EXTRACTED_DATA_PATH)
}

AUTHOR_DATA = AUTHOR_DATA %>% mutate(
  ShortName = ShortName %>%
           str_replace("& Preg", "&\nPreg") %>%
           str_replace("& Surv", "&\nSurv") %>%
           str_replace("& Diag", "&\nDiag")
)

# ggplot theme
ggtheme = theme_cowplot()
theme_set(ggtheme)

source("plot-functions.R")
```

Add info about the FAPERJ Network to which the authors belong.
```{r}
FAPERJ_NETWORK_INFO = read_excel("../../data/institutions/FAPERJ_Networks.xlsx")
```


## Characterization of the authors who published in Zika

### Description of Most Common Journal Area before Epidemics
```{r}
plot_most_common_areas(AUTHOR_DATA, period = "Pre-Outbreak", min_thres = 0)
```


### Academic Age - Years Since the First Paper Record
```{r}
plot_academic_age_hist(AUTHOR_DATA, period = "Pre-Outbreak")
```

### Total Citations, before Epidemics
```{r}
plot_total_citations(AUTHOR_DATA, period = "Pre-Outbreak", logscale = F)
plot_total_citations(AUTHOR_DATA, period = "Pre-Outbreak", logscale = T)
```

## Changes in publication patterns after the outbreak

### Citations per Paper, before and Zika papers
```{r}
plot_compare_citations_per_paper(AUTHOR_DATA)
```

### Number of Authors per Paper, before and Zika papers
```{r}
plot_compare_authors_per_paper(AUTHOR_DATA)
```


### Percentage of Papers with International Affiliations, before and Zika papers
```{r}
plot_compare_intl_papers(AUTHOR_DATA)
```

### Percentage of Zika-related papers post 2016
```{r}
plot_perc_zika_papers(AUTHOR_DATA)
```

## Characterization of Zika-related publications

### Frequency of MeSH Categories

```{r}
plot_pubs_by_mesh_cat(AUTHOR_DATA, title = "All Fields")
```
### Citations by MeSH category

```{r}
plot_cites_by_mesh_cat(AUTHOR_DATA)
```

### Citations per paper, by MeSH category

```{r}
plot_cite_rate_by_mesh_cat(AUTHOR_DATA)
```

## Characterization of Zika-related publications, for each FAPERJ network

### Frequency of MeSH Categories

```{r}
plot_pubs_by_mesh_cat_FAPERJ(AUTHOR_DATA, FAPERJ_NETWORK_INFO)
```
### Citations by MeSH category

```{r}
plot_cites_by_mesh_cat_FAPERJ(AUTHOR_DATA, FAPERJ_NETWORK_INFO)
```

### Citations per paper, by MeSH category

```{r}
plot_cite_rate_by_mesh_cat_FAPERJ(AUTHOR_DATA, FAPERJ_NETWORK_INFO)
```

